03_DESeq_pit

### 2019-04-05 analysis/03_DESeq2_pit.Rmd
deseq2 attempts

---
title: "02_DESeq_hyp"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/hyp/',cache=TRUE)
```

@@

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('hypothalamus', tissue)) %>%
  #dplyr::filter(treatment != "control") %>%
  dplyr::filter(sex == "female") %>%
  droplevels()
row.names(colData) <- colData$V1

@@

```{r res}
levels(colData$treatment)
summary(results(dds, contrast=c("treatment",'control', 'bldg')))    #3502 2450
summary(results(dds, contrast=c("treatment",'control', 'lay')))     #3581 2642
summary(results(dds, contrast=c("treatment",'control', 'inc.d3')))  #3956 2802
summary(results(dds, contrast=c("treatment",'control', 'inc.d9')))  #3968 2985
summary(results(dds, contrast=c("treatment",'control', 'inc.d17'))) #3949 2724
summary(results(dds, contrast=c("treatment",'control', 'hatch')))   #3600 2660
summary(results(dds, contrast=c("treatment",'control', 'n5')))      #4080 2842
summary(results(dds, contrast=c("treatment",'control', 'n9')))      #4035 2979

summary(results(dds, contrast=c("treatment",'bldg', 'lay')))     #1   0
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d9')))  #5   0 
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d17'))) #0   0 
summary(results(dds, contrast=c("treatment",'bldg', 'hatch')))   #1   2
summary(results(dds, contrast=c("treatment",'bldg', 'n5')))      #10  3
summary(results(dds, contrast=c("treatment",'bldg', 'n9')))      #168 124

summary(results(dds, contrast=c("treatment",'lay', 'bldg')))    #    1
summary(results(dds, contrast=c("treatment",'lay', 'inc.d3')))  #0   0   
summary(results(dds, contrast=c("treatment",'lay', 'inc.d9')))  #5   6 
summary(results(dds, contrast=c("treatment",'lay', 'inc.d17'))) #2   2 
summary(results(dds, contrast=c("treatment",'lay', 'hatch')))   #3   8 
summary(results(dds, contrast=c("treatment",'lay', 'n5')))      #1   0
summary(results(dds, contrast=c("treatment",'lay', 'n9')))      #135 194

summary(results(dds, contrast=c("treatment",'inc.d3', 'bldg')))    #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))     #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d9')))  #1 0
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d17'))) #0 0   
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))     #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'n5')))      #0 0 
summary(results(dds, contrast=c("treatment",'inc.d3', 'n9')))      #0 0

summary(results(dds, contrast=c("treatment",'inc.d9', 'inc.d17'))) #2 3  
summary(results(dds, contrast=c("treatment",'inc.d9', 'lay')))     #6 5
summary(results(dds, contrast=c("treatment",'inc.d9', 'n5')))      #0 1
summary(results(dds, contrast=c("treatment",'inc.d9', 'n9')))      #0 2

summary(results(dds, contrast=c("treatment",'inc.d17', 'lay'))) #2   2
summary(results(dds, contrast=c("treatment",'inc.d17', 'n5')))  #2   4
summary(results(dds, contrast=c("treatment",'inc.d17', 'n9')))  #131 136

summary(results(dds, contrast=c("treatment",'hatch', 'bldg')))    #2   1    
summary(results(dds, contrast=c("treatment",'hatch', 'lay')))     #8   3  
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d3')))  #524 406 
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d9')))  #1106 1169 
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d17'))) #3    0 
summary(results(dds, contrast=c("treatment",'hatch', 'n5')))      #1076 875
summary(results(dds, contrast=c("treatment",'hatch', 'n9')))      #898  845

summary(results(dds, contrast=c("treatment",'n5', 'bldg')))    #3   10 
summary(results(dds, contrast=c("treatment",'n5', 'lay')))     #0   1 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d9')))  #1   0 
summary(results(dds, contrast=c("treatment",'n5', 'inc.d17'))) #4   2 
summary(results(dds, contrast=c("treatment",'n5', 'hatch')))   #875 1076 
summary(results(dds, contrast=c("treatment",'n5', 'n9')))      #0   0

summary(results(dds, contrast=c("treatment",'n9', 'bldg')))    #124 168 
summary(results(dds, contrast=c("treatment",'n9', 'lay')))     #194 135 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d3')))  #0   0 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d9')))  #2   0 
summary(results(dds, contrast=c("treatment",'n9', 'inc.d17'))) #136 131 
summary(results(dds, contrast=c("treatment",'n9', 'hatch')))   #845 898 
summary(results(dds, contrast=c("treatment",'n9', 'n5')))      #0   0 
```

@@

```{r}
summary(aov(PC1 ~ treatment, data=pcadata)) 
TukeyHSD(aov(PC1 ~ treatment, data=pcadata), which = "treatment")

@@

summary(aov(PC5 ~ treatment, data=pcadata)) 
TukeyHSD(aov(PC5 ~ treatment, data=pcadata), which = "treatment")

>>>>

---
title: "03_DESeq_pit"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/pit/',cache=TRUE)
```

@@

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('pituitary', tissue)) %>%
  #dplyr::filter(treatment != "control") %>%
  dplyr::filter(sex == "female") %>%
  droplevels()
row.names(colData) <- colData$V1

@@

```{r res}
levels(colData$treatment)
summary(results(dds, contrast=c("treatment",'control', 'bldg'))) 
summary(results(dds, contrast=c("treatment",'control', 'lay')))     
summary(results(dds, contrast=c("treatment",'control', 'inc.d3')))  
summary(results(dds, contrast=c("treatment",'control', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'control', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'control', 'hatch')))    
summary(results(dds, contrast=c("treatment",'control', 'n5')))      
summary(results(dds, contrast=c("treatment",'control', 'n9')))

summary(results(dds, contrast=c("treatment",'bldg', 'lay')))      
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d3')))   
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'bldg', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'bldg', 'hatch')))   
summary(results(dds, contrast=c("treatment",'bldg', 'n5')))      
summary(results(dds, contrast=c("treatment",'bldg', 'n9')))

summary(results(dds, contrast=c("treatment",'lay', 'bldg')))     
summary(results(dds, contrast=c("treatment",'lay', 'inc.d3')))    
summary(results(dds, contrast=c("treatment",'lay', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'lay', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'lay', 'hatch')))    
summary(results(dds, contrast=c("treatment",'lay', 'n5')))       
summary(results(dds, contrast=c("treatment",'lay', 'n9')))

summary(results(dds, contrast=c("treatment",'inc.d3', 'bldg')))     
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))       
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'inc.d3', 'inc.d17')))   
summary(results(dds, contrast=c("treatment",'inc.d3', 'lay')))      
summary(results(dds, contrast=c("treatment",'inc.d3', 'n5')))        
summary(results(dds, contrast=c("treatment",'inc.d3', 'n9')))

summary(results(dds, contrast=c("treatment",'inc.d9', 'inc.d17')))   
summary(results(dds, contrast=c("treatment",'inc.d9', 'lay')))      
summary(results(dds, contrast=c("treatment",'inc.d9', 'n5')))       
summary(results(dds, contrast=c("treatment",'inc.d9', 'n9')))

summary(results(dds, contrast=c("treatment",'inc.d17', 'lay')))  
summary(results(dds, contrast=c("treatment",'inc.d17', 'n5')))   
summary(results(dds, contrast=c("treatment",'inc.d17', 'n9')))

summary(results(dds, contrast=c("treatment",'hatch', 'bldg')))      
summary(results(dds, contrast=c("treatment",'hatch', 'lay')))       
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d3')))    
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d9')))    
summary(results(dds, contrast=c("treatment",'hatch', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'hatch', 'n5')))       
summary(results(dds, contrast=c("treatment",'hatch', 'n9')))

summary(results(dds, contrast=c("treatment",'n5', 'bldg')))      
summary(results(dds, contrast=c("treatment",'n5', 'lay')))       
summary(results(dds, contrast=c("treatment",'n5', 'inc.d3')))  
summary(results(dds, contrast=c("treatment",'n5', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'n5', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'n5', 'hatch')))   
summary(results(dds, contrast=c("treatment",'n5', 'n9')))

summary(results(dds, contrast=c("treatment",'n9', 'bldg')))     
summary(results(dds, contrast=c("treatment",'n9', 'lay')))      
summary(results(dds, contrast=c("treatment",'n9', 'inc.d3')))   
summary(results(dds, contrast=c("treatment",'n9', 'inc.d9')))   
summary(results(dds, contrast=c("treatment",'n9', 'inc.d17')))  
summary(results(dds, contrast=c("treatment",'n9', 'hatch')))    
summary(results(dds, contrast=c("treatment",'n9', 'n5')))     
```

@@

```{r pcastats}
summary(aov(PC1 ~ treatment, data=pcadata)) 
TukeyHSD(aov(PC1 ~ treatment, data=pcadata), which = "treatment")

@@

summary(aov(PC5 ~ treatment, data=pcadata))
